Packaging research artefacts with RO-Crate

### 2022-01-02 latex/ro-crate.tex
break sentence

The Root Data Entity is a directory, the \textit{RO-Crate Root}, identified by
the presence of the \textbf{RO-Crate Metadata File} \texttt{ro-crate-metadata.json}
(top of Fig.~\ref{fig:conceptual}). This file
describes the RO-Crate, its content and related metadata using Linked
Data in JSON-LD format \cite{sporny_2014}. This is a W3C standard RDF serialisation that has become
popular as it is easy to read by humans while also offers some
advantages for data exchange on the Internet. JSON-LD, a subset of the
widely supported and well-known JSON format, has tooling available for
many programming languages.\footnote{\url{https://json-ld.org/\#developers}}

>>>>

The Root Data Entity is a directory, the \textit{RO-Crate Root}, identified by
the presence of the \textbf{RO-Crate Metadata File} \texttt{ro-crate-metadata.json}
(top of Fig.~\ref{fig:conceptual}). This file
describes the RO-Crate, its content and related metadata using Linked
Data in JSON-LD format \cite{sporny_2014}. This is a W3C standard RDF serialisation that has become
popular; it is easy to read by humans while also offering some
advantages for data exchange on the Internet. JSON-LD, a subset of the
widely supported and well-known JSON format, has tooling available for
many programming languages.\footnote{\url{https://json-ld.org/\#developers}}
